\vspace*{2cm}
% Abstract

\vspace{10ex}
{\bf\Large Abstract} \\ [1em]
Cyber-physical systems become highly popular in people's everyday life. One of these systems are self-driving vehicles in automotive industry. To design and develop that kind of systems, component and connector (C\&C) models are widely used. This thesis focuses on creating a tool supporting the learning process of C\&C modeling principles. EmbeddedMontiArc has been chosen as one of the most advanced C\&C modelling languages. Furthermore, it is not sufficient to have an environment for the development, it is important to have enthralling tutorials which reveal all advantages of the C\&C modeling. The presented tutorials apply the gamification principles, which become popular nowadays through a good learning outcome. To build a comprehensive teaching tool, we analysed existing tutorials and playgrounds, to derive important requirements for the future product. Based on the derived requirements, an architecture is created and implementation of components is given. Moreover, technologies that were used during the development process are explained in details. Later, it is clarified how to use the environment to achieve high productivity during the learning process. Finally, this thesis presents a group of tutorials, with real examples and step-by-step solutions. To try the tutorials online, the following link should be used \cite{OnlineExample}. The article, which describes the toolchain with tutorials \cite{TeachPlay}, was published on the fifth International Workshop on Interplay of Model-Driven and Component-Base Software Engineering.